% !TeX root=main.tex
% در این فایل، عنوان پایان‌نامه، مشخصات خود و چکیده پایان‌نامه را به انگلیسی، وارد کنید.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\baselineskip=.6cm
\begin{latin}
\latinuniversity{Iran University of Science and Technology}
\latinfaculty{Computer Engineering Department}
\latinsubject{Computer Engineering - Software Engineering}
\latinfield{Software Engineering}
\latintitle{A K8-Based Mechanism for Remote Monitoring and Control of IoT Devices}
\firstlatinsupervisor{Dr. Mohsen Sharifi}
%\secondlatinsupervisor{Second Supervisor}
% \firstlatinadvisor{First Advisor}
%\secondlatinadvisor{Second Advisor}
\latinname{Sina}
\latinsurname{Shabani Kumeleh}
\latinthesisdate{Summer 2023}
\latinkeywords{Internet of Things, Kubernetes, Virtual Kubelet, Centeralized Monitoring, Scalable Monitoring}
\en-abstract{
  In today's world, the management, control and supervision of IoT devices 
  face a significant challenge. The lack of a unified solution hinders 
  effective control and monitoring of a diverse range of IoT devices. 
  This results in fragmented control mechanisms and complex management processes. 
  The project 
  "A K8-Based Mechanism for Remote Monitoring and Control of IoT Devices" 
  proposes an innovative approach to address this challenge. 
  By leveraging the capabilities of Kubernetes as the core infrastructure, 
  the project aims to provide a comprehensive solution for centralized control
   and monitoring of IoT devices. This solution streamlines the management 
   process and enhances efficiency by offering a unified platform for device 
   control and monitoring. With its robust architecture, the project facilitates
    seamless integration, scalability, and intelligent decision-making based on
     real-time device data. By implementing this solution, organizations can
      effectively manage and monitor their IoT device ecosystem while optimizing
       operations and ensuring optimal performance.
}
\latinfirstPage
\end{latin}
